---
title: "Exam 2: R Basics"
tutorial:
  id: "Week_6_Exam_2"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
description: "Exam testing your knowledge of the basics of R"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(tutorial.helpers)
knitr::opts_chunk$set(echo = FALSE)

#play around with the answer_fn
# answer_fn_silent <- function(submitted) {
#   list(message = NULL, correct = TRUE)  # No feedback
# }

gradethis::gradethis_setup(
  code_correct = "Submitted",
  code_incorrect = "Submitted",
)

```

```{r, include=FALSE}
#Author: Andrew J. Felton
#Date: 2/14/2025
```

## Directions

### This test will be 71 points and will be taken within this R tutorial. The test will be a mix of  free response and writing R code in response to prompts, much like you have been doing the past two weeks. You will submit the exam as .html file on D2L, just as you hjave been doing the past three weeks. You will be graded on correctness for every answer and partial credit will be given when warranted.

## Q's 1-9:Free Response (18 points: 2 points each)

```{r problem_1}

  question_text(
    "Q1: What operator is your first line of defense if you are unsure about what a function is or does or how it works in R? (1 point)",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_2}

  question_text(
    "Q2: What is the purpose of the `<-` operator?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_3}

  question_text(
    "Q3: What is the purpose of the `!=` operator?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_4}

  question_text(
    "Q4: True or False: all values in an atomic vector are composed of the same data type",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_5}

  question_text(
    "Q5: True or False: all values in an atomic vector are composed of the same data type",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_6}

  question_text(
    "Q6: What does the c() function do?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_7}

  question_text(
    "Q7: If you add 1:7 to c(0,1), what will the fifth value be?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_8}

  question_text(
    "Q8: In the question above, what concept is this an example of?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```

```{r problem_9}

  question_text(
    "Q9: Which characteristic(s) of tidy data is not always an atomic vector?",
  answer("", correct = TRUE),
  allow_retry = FALSE,
  rows=3,
  trim = FALSE,
  answer_fn(learnr::correct),
  correct = "Your answer has been submitted for grading.",
  incorrect = "Your answer has been submitted for grading."
)

```


## Q's 10-16: Coding (53 points total)

### Q10: Create a numeric vector from 1 to 1000 that increases by values of 5. Name this vector "vector_1". (5 points)

```{r problem_10, exercise=TRUE,exercise.reveal_solution=FALSE}

```

```{r problem_10-solution,exercise.reveal_solution=FALSE}
vector_1 <- seq(from = 1,to = 1000,by = 5)
```

```{r problem_10-check}
grade_this_code()
```
### Q11: Use recycling to reduce every value in vector_1 by 50%. Name this new vector "vector_1_halved". Then, create an x-y plot with vector_1 on the x axis and vector_1_halved on the y axis. (10 points)


```{r problem_11, exercise=TRUE, exercise.setup="problem_10"}

```

```{r problem_11-solution,exercise.reveal_solution=FALSE}
vector_1_halved <- vector_1*0.5
plot(x = vector_1,y = vector_1_halved)
```

```{r problem_11-check}
grade_result(default_message = "submitted")
```


### Q12: Create a dataframe that is composed of three columns: 1) a column named 'Production' that is a numeric vector composed of the values 750,500,and 250, 2) a column named 'Precipitation' that is a numeric vector composed of the values 1200, 700, and 200, and 3) a column named 'Biome' that is a character vector composed of the values "Forest","Grassland", and "Desert". Assign this new dataframe the name "NPP". (20 points)

```{r problem_12, exercise=TRUE}

```

```{r problem_12-solution,exercise.reveal_solution=FALSE}
NPP <- data.frame(
  Production = c(750,500,250),
  Precipitation = c(1200,700,200),
  Biome = c("Forest","Grassland","Desert")
)
```

```{r problem_12-check}
grade_code()
```

### Q13: Use an extraction operator to preview the first row of the NPP dataframe you created in Q17 (while retaining all column names). (2 points)

```{setup_3,include=F}


```

```{r problem_13, exercise=TRUE, exercise.setup="problem_12"}

```

```{r problem_13-solution,exercise.reveal_solution=FALSE}
NPP[1,]
```

```{r problem_13-check}
grade_code()
```

### Q14: Use an extraction operator to add a new column to the NPP dataframe called 'RUE' that is calculated as production divided by precipitation. This variable describes how efficiently rainfall is used for plant growth. (5 points)

```{r problem_14, exercise=TRUE,exercise.setup="problem_12"}

```

```{r problem_14-solution,exercise.reveal_solution=FALSE}
NPP$RUE <- NPP$Production/NPP$Precipitation
```

```{r problem_14-check}
grade_code()
```

### Q15: Using the NPP dataframe, create an x-y plot that depicts how RUE changes as a response to precipitation. You can use *either* of the two approaches (but, within the same function!) to do this that were discussed in class. (5 points)

```{r problem_15, exercise=TRUE,exercise.setup="problem_14"}

```

```{r problem_15-solution,exercise.reveal_solution=FALSE}
plot(RUE ~ Precipitation,data = NPP)
#plot(NPP$Precipitation,NPP$Production) is also valid
```

```{r problem_15-check}
grade_code()
```

### Q16: Use the `data()` function to load in the iris dataframe that comes with R and then use both extraction and comparison operators to filter the iris dataframe to *just* the setosa species. Name this new dataframe iris_setosa. (6 points)
```{r problem_16, exercise=TRUE}

```

```{r problem_16-solution,exercise.reveal_solution=FALSE}
data(iris)
iris_setosa <- iris[iris$Species == 'setosa',]
```

```{r problem_16-check}
grade_code()
```

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```

All done! Please upload your html file in the correct assignment folder.
